---
title: "In Class Exercise 2"
author: "Joshua L Eubanks"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readxl)
library(tidyverse)
```

# Wealth of 1 Percent

This dataset was obtained from FRED which shows the share of total net worth held by the top 1%. It is represented over time.

```{r wealth}
Wealth1percent <- read_excel("~/Documents/ECO6416/ECO6416/Data/Wealth1percent.xlsx")
View(Wealth1percent) 
col_types = c("date","numeric","numeric")

colnames(Wealth1percent)[3] <- "TimeCounter"

```

This gives us a range of data from the third quarter of 1989 to the first quarter of 2021

## Time Series Plot


```{r wealthplot , message=F}
plot(Wealth1percent$quarter, Wealth1percent$Share,
     main = "Scatterplot of 1%",
     xlab = "TimeCounter",
     ylab = "Share")
abline(lm(Share ~ TimeCounter, data = Wealth1percent),lty = 2, col = "green")
```


## Time Series Regression

We can see the trend in an upwards manner, let's see what the quarterly change in slope is:

```{r wealth regression}
wealthregression <- lm(Share ~ TimeCounter, data = Wealth1percent)

wealthregression$coefficients[2]

summary(wealthregression)
```

in this case, the share of wealth held by the top 1% is increasing by 0.05% each quarter.

## Prediction

Suppose we want to predict the share of wealth 2 quarters form now:

```{r}
newpredictions <- data.frame(TimeCounter = 133)

predict(wealthregression, newdata = newpredictions, interval = "confidence", level = .8)
```


# Covid cases NYT

This data was pulled for March 2020 for covid cases in the US

```{r}

```

## Plot

```{r}


```

## Regression

```{r}

```


## Prediction

What would be the predicted number of cases by April 15, 2020?

```{r}

```

## Thing 2 

On average, how many new cases of covid are there daily?

```{r}


```

